\documentclass[a4paper,11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[margin=1.0in]{geometry}
\usepackage{pdflscape}

\author{Abdulaziz Alsa{f}far and Abdulrahman Alotaibi}
\title{Full-Stack Development Plan - Executive Summary}

\begin{document}
\maketitle
\pagestyle{plain}
\setcounter{page}{1}
\pagenumbering{arabic}

\section{Executive Summary}

\paragraph{}
The following forms highlight the proposed plan for a four-week, three-phase, in-house training program for KISR developers. The purpose of these courses is to establish a modern software engineering approach here at KISR. The goal is to give KISR developers the tools they need to work in teams to tackle larger projects from start to end efficiently and effectively.

\paragraph{}
The course consists of three phases:
\begin{itemize}
	\item Phase 1 - Developer Tools\\1 Week\\This is an introduction to the essential basic develeopment tools and environments.
	\item Phase 2 - Team Project Workflow\\1 Week\\This is a workshop about the process of contributing and managing multi-developer projects.
	\item Phase 3 - Complete Web Development\\2 Weeks\\This is a workshop about the processes and practices of modern web development.
\end{itemize}

\paragraph{}
Each phase will be submitted as an independent in-house training course; however, the assumption is that the phases build on one another. The tools that participants are taught to use in Phase 1 are considered prerequisites for Phase 2. Phase 3 is a longer course because participants will take all the material from previous phases and apply it in a team project.

\paragraph{}
Participants in this course are expected to have previous programming experience. The course is pitched at participants with a computing background. The primary purpose of the course is to introduce developers to new software engineering and development paradigms. This course does \textbf{not} teach any programming or coding concepts.

\pagebreak

\section{Instructor Resumes}
\subsection{Abdulrahman Alotaibi}
Abdulrahman recently graduated from \textsc{Old Dominion University, Virginia} with a \textsc{dual degree} in \textsc{Computer Engineering} and \textsc{Electrical Engineering} with a minor in \textsc{Computer Science}. He has an extensive background when it comes to \textsc{programming} and \textsc{software development} and has joined many conferences, hackathons and competitions. Abdulrahman is currently one of the organisers of the Kuwait chapter of the \textsc{Google Developers Group}.

\subsection{Abdulaziz Alsa{f}far}
Abdulaziz has an \textsc{MSc in Intelligent Systems} from \textsc{King's College London} and a \textsc{BEng(Hons) in Computer Systems Engineering} from \textsc{Curtin University, Western Australia}. He has a strong theoretical background in \textsc{algorithm design} and experience with \textsc{robotics and lab automation}. Abdulaziz is currently an active member of the Kuwait chapter of the \textsc{Google Developers Group}.

\end{document}
