\documentclass[a4paper,11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[margin=1.0in]{geometry}

\author{Abdulaziz Alsa{f}far and Abdulrahman Alotaibi}
\title{In-House Course Design Form}

\begin{document}
\maketitle
\pagestyle{plain}
\setcounter{page}{1}
\pagenumbering{arabic}

\section{Course Title:}
TODO pick one or add suggestions
\begin{itemize}
    \item The Development Environment
    \item Introduction to Developer Tools
    \item Full-Stack engineering part I
\end{itemize}

\section{Purpose:}
The purpose of this course is to introduce the participants to the basics tools used in most software development environments.
Participants will gain knowledge about when, how, and how best to utilise these core development tools. 
The participants will gain experience in setting up their own environment, selecting the tools they need, and e{f}ficiently navigating through their workspace. Also, participants will know how they work ef{}ficiently in teams of developers.

\section{Course Objectives:}
TODO approve or change order
\begin{itemize}
	\item Set up and manage Virtual Machines
	\item Use Bash and the Command Line Interface
	\item Select, retrieve, install, and generally manage software packages
	\item Understand the use of Integrated Development Environments
	\item Use command line editors
	\item Select between various documentation software
\end{itemize}

\section{Course Topics:}
TODO approve or change order
\begin{itemize}
	\item Virtual Machines
	\item The Command Line Interface
	\item Package Managers
	\item Editors and Integrated Development Environments
	\item Documentation
\end{itemize}

\section{Training Methods:}
\begin{itemize}
	\item Demonstrations
	\item Practical Sessions
	\item Toy Project
\end{itemize}

\section{Participants:}
This course is for people who will be working on projects that require software development at any level. These tools will be useful for those working on both individual and team projects, from the minimal single-{f}ile scripting project to a complete software engineering project. These tools should help all developers and programmers. The minimum requirement is a coding and programming background.\\
This course will NOT teach any formal programming in any language!

\section{Prerequisites:}
Participants are expected to have a coding and programming background. Also, participants should have their own laptops or a machine that they have administrative rights to it.

\section{Course Date, Duration and Timings:}
Date: TODO\\
Duration: 1 Week\\
Timings: 9am-12pm


\end{document}
